Exploiting the Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-25 2017-CEC-Graph-Based-Population-For- IEC/paper.tex

As a case study, a IEA was developed using the 
EvoSpace-Interactive (ES-I) platform \cite{garcia2013evospace}. %citation
A brief description of the application is presented next, focusing
on the data elements that where ported to the graph model.

\subsection{Fitness Assignment}
\label{sec:assignment}
The ES-I platform employs a collaborative technique,
where several registered users assign a quality assessment to a single
individual and then an aggregated fitness value is calculated. The fitness
assigned to each individual depends on the taste of each particular user, 
resulting in a many-to-many relationship between users and individuals. 
Many systems query this user-individual relation to extract relevant
knowledge about the process and the population, for instance showing the
most popular individual, or the the user with more participation 
\cite{picbreeder}.
In order to do this, data about individuals 
must be permanently stored, even
if they are no longer in the active population.

@@

\item Participation. This value is simply the degree of the user node 
in the graph. This measure also considers the number of users he knows,
perhaps some of the users where invited to the system by him.   
\end{itemize}

Three versions were compared:
\begin{itemize}
\item Base (B). All users have the same weight.
\item Non Graph Gamification (G). Only experience is considered
\item Graph Gamification (GG) . Both experience and participation are considered.
\end{itemize}
When gamification was employed, all score values known where presented to users
and a ranking of users by weight was shown in a window, a screen capture of
this interface is shown in figure \ref{fig:top-users}.

>>>>

As a case study, a IEA was developed using the 
EvoSpace-Interactive (ES-I) platform \cite{garcia2013evospace}. %citation
A brief description of the application is presented next, focusing
on the data elements that were ported to the graph model.

\subsection{Fitness Assignment}
\label{sec:assignment}
The ES-I platform employs a collaborative technique,
where several registered users assign a quality assessment to a single
individual and then an aggregated fitness value is calculated. The fitness
assigned to each individual depends on the taste of each particular user, 
resulting in a many-to-many relationship between users and individuals. 
Many systems query this user-individual relation to extract relevant
knowledge about the process and the population, for instance showing the
most popular individual, or the the user with more participation.  
\cite{picbreeder}.
In order to do this, data about individuals 
must be permanently stored, even
if they are no longer in the active population.

@@

\item Participation. This value is simply the degree of the user node 
in the graph. This measure also considers the number of users he knows,
perhaps some of the users were invited to the system by him.   
\end{itemize}

Three versions were compared:
\begin{itemize}
\item Base (B). All users have the same weight. Still the graph is used internally to explore
the social network and the evolution of the population.
\item Non Graph Gamification (G). Only experience is considered for the reputation of users. 
\item Graph Gamification (GG). Both experience and participation are considered.
\end{itemize}
When gamification was employed, all score values known were presented to users
along with a ranking of users by their weight was shown in a window, as an example
a screen capture of this interface is shown in figure \ref{fig:top-users}.
